---
title: "Computational Analysis Single cell RNA-seq"
author: "Ben Babcock"
date: "03/25/2019"
output: html_document
fig_width: 6 
fig_height: 5 
message: False
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import Expression Matrix
###Format Objects
###Add MetaData
```{r}
source("~/SingleCell.Utilities.R")
mice <- paste0("B", c(1:8, "9-1", "9-2", 14:15))
seurats <- list()

min.genes <- 10
min.cells <- 0
prep.Seurat <- function(i){
  message('Starting with Sample ', i)
  df <- fread(paste0('/pine/scr/s/e/seth96/BCL/', i, '/out/dge.txt'),
              stringsAsFactors = F, 
              data.table = F, sep = "\t", header = T)
  rownames(df) <- df$GENE
  df$GENE <- NULL
  colnames(df) <- paste(as.character(i), colnames(df), sep="_")
  dat <- CreateSeuratObject(counts = df,
                                       min.cells = min.cells,
                                       min.features = min.genes)
  dat <- StashIdent(object = dat,
                    save.name = "Replicate")
  return(dat)
}

seurats <- lapply(mice, function(x) prep.Seurat(x))
names(seurats) <- mice

BCL <- MergeSeurat(seurats[['B1']], seurats[['B2']])
for(mouse in mice[3:length(mice)]){
  BCL <- MergeSeurat(BCL, seurats[[mouse]])
}

Treatment <- c("Vehicle", "Vehicle", "Vehicle", 
               "Vehicle", "Vehicle",
               "Vismodegib", "Vismodegib", "Vismodegib", 
               "Vismodegib", "Vismodegib")
Sex <- c("Female", "Female", "Male", "Male", "Male", 
         "Male", "Female", "Female", "Male", "Female")
Date <- c("July02", "July02", "July25", "July25", "August18", 
          "July02", "July25", "July25", "August18", "August18")
GT <- SetAllIdent(GT, "Replicate")
GT@ident <- plyr::mapvalues(x = GT@ident, from = mice, to = Treatment)
GT <- StashIdent(object = GT, save.name = 'Treatment')
GT <- SetAllIdent(object = GT, id = "Replicate")
GT@ident <- plyr::mapvalues(x = GT@ident, from = mice, to = Sex)
GT <- StashIdent(object = GT, save.name = 'Sex')
GT <- SetAllIdent(object = GT, id = "Replicate")
GT@ident <- plyr::mapvalues(x = GT@ident, from = mice, to = Date)
GT <- StashIdent(object = GT, save.name = 'Date')
GT <- SetAllIdent(object = GT, id = "Replicate")
```
#Apply Data Quality Filters
###(Many are data-set specific, owing to differing depths of sequence by library batch)
```{r}
mito.genes <- grep(pattern = "^mt-", x = rownames(GT@data), value = TRUE)
percent.mito <- (Matrix::colSums(GT@raw.data[mito.genes,])/Matrix::colSums(GT@raw.data))*100
GT <- AddMetaData(object = GT, metadata = percent.mito, col.name = "percent.mito")

VlnPlot(object = GT, 
        features.plot = c("nGene", "nUMI", "percent.mito"), nCol = 3, group.by = "Date")

seurats <- list()

seurats[['MB04']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(2500, 5000, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB04"))
seurats[['MB05']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(2000, 4000, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB05"))
seurats[['MB06']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(3000, 5000, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB06"))
seurats[['MB07']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(2200, 4000, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB07"))
seurats[['MB09']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(4000, 7500, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB09"))
seurats[['MB10']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(3000, 7200, 5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB10"))
seurats[['MB12']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(4000, 10000, 7.5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB12"))
seurats[['MB13']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(4000, 10000, 7.5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB13"))
seurats[['MB14']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(4000, 10000, 7.5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB14"))
seurats[['MB15']] <- FilterCells(object = GT, 
                  subset.names = c("nGene", "nUMI", "percent.mito"), 
                  low.thresholds = c(500, 200, -Inf), 
                  high.thresholds = c(4000, 10000, 7.5),
                  cells.use = WhichCells(GT, subset.name = "Replicate",
                                         accept.value = "MB15"))

GT <- MergeSeurat(seurats[[mice[1]]], seurats[[mice[2]]])
for(mouse in mice[3:length(mice)]){
  GT <- MergeSeurat(GT, seurats[[mouse]])
}

VlnPlot(object = GT,group.by = "Date", features.plot = c("nGene", "nUMI", "percent.mito"), nCol = 3)
```
#Investigate Large Data Set by tSNE & Clusters

```{r}
# Data scaling is better done with the maximum number of cells - we keep all cells here.
# Treatment-specific analyses will be performed following the text workflow following.
#Save all raw data prior to filtering genes by number of cells detected
GT@misc <- GT@raw.data
#Filter genes by minimum number of cells with that transcript detected
GT@raw.data  <- GT@raw.data[rowSums(GT@raw.data != 0) >= 30, ]
#Follow Seurat HVG selection
GT <- NormalizeData(GT)
GT <- FindVariableGenes(GT, x.low.cutoff = 0.0125, 
                        x.high.cutoff = 3, 
                        y.cutoff = 0.5, 
                        y.high.cutoff = Inf, 
                        num.bin = 20)
#Apply linear scaling & centering to data
GT <- ScaleData(GT, vars.to.regress = 'nUMI')
```
###Seurat Workflow
```{r}
#Predict the number of significant PCs (Z-score variance > 2)
GT.pca <- TestPCA(GT, do.return = T)
GT <- RunPCA(GT, pcs.compute = 60, seed.use = 42, weight.by.var = T, rev.pca = F, use.imputed = F)
#Find cluster populations & tSNE coordinates for visualization
GT <- FindClusters(GT, dims.use = 1:10, resolution = 1, 
                   k.param = 30, random.seed = 0)
GT <- StashIdent(GT, "GTClust")
GT <- RunTSNE(GT, dims.use = 1:10, seed.use = 1, tsne.method = "Rtsne")
for(ident in c("Treatment", "Sex", "Date", "GTClust")){
  GT <- SetAllIdent(GT, ident)
  TSNEPlot(GT, plot.title = ident)
}

writeMarkers <- function(object, ident, file.path){
  message('Finding Markers of ', ident)
  markers <- FindMarkers(object, ident.1 = ident)
  message('Writing Markers of ', ident)
  write.xlsx(markers, file.path, sheetName = paste0("Clust_", ident), append = T)
}

#lapply(0:17, function(i) writeMarkers(GT, i, "MB_Markers.xlsx"))
```
###Filter out doublet clusters
```{r}
# Doublets are identified by broad expression of conflicting markers.
# Usually with low (scaled) levels of transcript detected, and often biased towards few replicates
GT <- SetAllIdent(GT, "GTClust")
TSNEPlot(GT, colors.use = colors.use)
#Theses steps must be done interactively
#to.remove <- TSNEPlot(GT, do.identify = T, 
#                     cells.use = WhichCells(GT, subset.name = "GTClust", 
#                                            accept.value = 11))

#to.remove <- c(to.remove, WhichCells(GT, 
#                                     subset.name = "GTClust", 
#                                     accept.value = 17))
#to.keep <- WhichCells(GT)[!(WhichCells(GT) %in% to.remove)]
GT2 <- readRDS("GT.rds")
GT <- SubsetData(GT, cells.use = WhichCells(GT2))
rm(GT2)
TSNEPlot(GT, colors.use = colors.use)
saveRDS(GT, "GT.rds")
```

#Begin characterizing Vehicle-only replicates
```{r}
Veh <- SubsetData(GT, subset.name = "Treatment", accept.value = "Vehicle")
Veh <- FindVariableGenes(Veh, x.low.cutoff = 0.05, 
                         x.high.cutoff = 5, 
                         y.cutoff = 0.5, 
                         y.high.cutoff = Inf, 
                         num.bin = 20,
                         do.plot = F)
Veh.pca <- TestPCA(Veh, Veh@var.genes, do.return = T)
Veh <- RunPCA(Veh, seed.use = 42, pcs.compute = 60)
VlnPlot(Veh, "PC10", group.by = "Date")
VlnPlot(Veh, "PC10", group.by = "Replicate")
#PC10 shows batch effect associated with both run date and mouse. We will ignore PC10 for the tSNE visualization
PrintPCA(Veh, 10)
Veh <- RunTSNE(Veh, reduction.use = 'pca', seed.use = 1, dims.use = c(1:9, 11))
# Plot tSNE with Clusters from Group Set
TSNEPlot(Veh, colors.use = colors.use)

# Plot tSNE with Clusters from Vehicle-only
# Fig. 2A
Veh <- FindClusters(Veh, dims.use = c(1:9, 11), resolution = 0.8)
Veh <- StashIdent(Veh, 'VehClust')
veh.colors <- colors.use[c(1:9, 13, 14, 12, 16, 15, 17)]
#devSVG("Fig.2A_Veh_tSNE_Clusters.svg")
TSNEPlot(Veh, colors.use = veh.colors)
#dev.off()

# Investigate Stromal Markers
# Fig. 2B
genes <- c("Col3a1", "C1qb", "Meg3", "Sox10", 'Aqp4', "Pecam1")
thresh <- c(3,3,4,1,3,2)
names(thresh) <- genes
colors2 <- colors.use[c(16, 14, 15, 13, 12, 17)]
#devSVG("Fig.2B_Veh_Stromal_Markers.svg")
MultiFeaturePlot(Veh, gene.list = genes, colors = colors2, threshold = thresh, pt.size = 1)
#dev.off()
```

###Organize Clusters
```{r}
# To better organize we want to isolate the solid tumor from the stroma
# Fig. 2C
Veh <- SetAllIdent(Veh, 'VehClust')
#devSVG("Fig.2C_Veh_HCA_Dendrogram.svg")
Veh <- BuildClusterTree(Veh, pcs.use = c(1:9, 11))
#dev.off()

# Fig. 2D
Veh@ident <- plyr::mapvalues(Veh@ident, from = levels(Veh@ident), 
                             to = c("Node_A", "Node_A", "Node_B", 
                                    "Node_B", "Node_B", "Node_C",
                                    "Node_C", "Node_C", "Node_A",
                                    "Oligodendrocytes", "Microglia",
                                    "Astrocytes", "Vascular_Fibroblasts",
                                    "Neurons", "Endothelial_Cells"))
Veh <- StashIdent(Veh, "VehNode")
vehIDs <- c("Node_A", "Node_B", "Node_C", "Neurons",
                      "Oligodendrocytes", "Astrocytes", "Microglia",
                      "Vascular_Fibroblasts", "Endothelial_Cells")
colors2 <- c(brewer.pal(5, "Paired")[c(5, 1, 3)], 
             colors.use[c(15, 13, 12, 14, 16, 17)])
#devSVG("Fig.2D_Nodes_projected_onto_t-SNE.svg")
TSNEPlot(Veh, colors.use = colors2, plot.order = rev(vehIDs))
#dev.off()

saveRDS(Veh, 'Veh.rds')
```

#Introduce Wild Type Cerebellum (at age P7)
###Preprocessing
```{r}
mice <- paste0("WT", c("01", "02", "03", "04", "05"))

seurats <- list()
min.genes <- 300
min.cells <- 0
prep.Seurat <- function(i){
  message('Starting with Sample ', i)
  df <- fread(paste0('../DGEs/', i, '.dge'),
              stringsAsFactors = F, data.table = F, 
              sep = "\t", header = T)
  rownames(df) <- df$GENE
  df$GENE <- NULL
  colnames(df) <- paste(as.character(i), colnames(df), sep="_")
  dat <- CreateSeuratObject(raw.data = df,
                                       min.cells = min.cells,
                                       min.genes = min.genes)
  dat <- StashIdent(object = dat,
                    save.name = "Replicate")
  return(dat)
}

seurats <- lapply(mice[1:5], function(x) prep.Seurat(x))
names(seurats) <- mice[1:5]

WT <- MergeSeurat(seurats[['WT01']], seurats[['WT02']])
for(mouse in mice[3:5]){
  WT <- MergeSeurat(WT, seurats[[mouse]])
}

WT@misc <- WT@raw.data
```
###Initial Filtering
```{r}
mito.genes <- grep(pattern = "^mt-", 
                   x = rownames(WT@raw.data), 
                   value = T)
percent.mito <- (Matrix::colSums(WT@raw.data[mito.genes, ])
                 /Matrix::colSums(WT@raw.data))*100
WT <- AddMetaData(object = WT, 
                  metadata = percent.mito, 
                  col.name = "percent.mito")
VlnPlot(WT, c("nUMI", "nGene", "percent.mito"), group.by = "Replicate")

WT <- SubsetData(WT, 
                 subset.name = 'nUMI', 
                 accept.high = 30000,
                 accept.low = 350)

max.UMI <- 4*sd(WT@meta.data$nUMI) + median(WT@meta.data$nUMI)
max.Gene <- 4*sd(WT@meta.data$nGene) + median(WT@meta.data$nGene)
max.mito <- sd(WT@meta.data$percent.mito)*5 + median(WT@meta.data$percent.mito)

WT <- SubsetData(WT, 
                 subset.name = 'nGene', 
                 accept.high = max.Gene,
                 accept.low = 500)
WT <- SubsetData(WT, 
                 subset.name = 'nUMI', 
                 accept.high = max.UMI,
                 accept.low = 600)
WT <- SubsetData(WT, 
                 subset.name = 'percent.mito', 
                 accept.high = max.mito)
WT@raw.data <- WT@raw.data[, WhichCells(WT)]

VlnPlot(WT, c("nUMI", "nGene", "percent.mito"), group.by = "Replicate")

WT <- NormalizeData(WT)
saveRDS(WT, 'CGNPs.raw.rds')
```
###Seurat workflow
```{r}
WT <- ScaleData(WT, vars.to.regress = c('nUMI'))
#HVG Selection
WT <- FindVariableGenes(WT, x.low.cutoff = 0.05, 
                        x.high.cutoff = 5, 
                        y.cutoff = 0.5, 
                        y.high.cutoff = Inf, 
                        num.bin = 40)
length(WT@var.genes)
#Select PCs
WT.pc.test <- TestPCA(WT, WT@var.genes, do.return = T)
WT.pc.test[, 1:20]
#Run n PCs
WT <- RunPCA(WT, pc.genes = WT@var.genes, pcs.compute = 60, 
             weight.by.var = T, use.imputed = F, seed = 42)
#Run tSNE for data visualization
WT <- RunTSNE(WT, reduction.use = 'pca', dims.use = 1:14, 
              perplexity = 30, seed.use = 1, tsne.method = "Rtsne",
              add.iter = 0)
#Check for strong batch effect in the tSNE
TSNEPlot(WT, colors.use = c(colors.use, more.colors))
#find clusters
WT <- FindClusters(WT, dims.use = 1:14, k.param = 7, resolution = 0.6, 
                   force.recalc = F)
WT <- StashIdent(WT, 'WildtypeClust')
getMarkers <- function(i){
  m <- FindMarkers(WT, i, test.use = 'bimod')
  colnames(m) <- c('p_val', 'avg_logFC', paste0('pct.clust', i), 
                   'pct.allOthers', 'p_val_adj')
  write.xlsx(m, file = 'CGNP_Markers.xlsx', sheetName = paste0('Cluster ', i), 
             append = T)
}

TSNEPlot(WT, colors.use = c(colors.use, more.colors))
#sapply(X = levels(WT@ident)[], FUN = function(i) getMarkers(i))
WT <- SubsetData(WT, ident.remove = 13)
# Label cells with canonical markers
# Fig. 3A

genes <- c("Col3a1", "C1qb", "Meg3", "Sox10", 'Aqp4', "Pecam1")
thresh <- c(3,3,4,1,3,1)
names(thresh) <- genes
colors2 <- colors.use[c(16, 14, 15, 13, 12, 17)]
p <- MultiFeaturePlot(WT, gene.list = genes, colors = colors2, threshold = thresh, pt.size = 1)
#devSVG('Fig.3A_WT_Stromal_Markers.svg')
p
#dev.off()

# Fig. 3B
colors2 <- brewer.pal(10,'Paired')[c(10, 4, 2, 6)]
thresh <- c(1,1,2,2)
names(thresh) <- c("Pax2", "Sox2", "Ascl1", "Pax3")
#devSVG('Fig.3B_WT_IP_Markers.svg')
MultiFeaturePlot(Object = WT, gene.list = c("Pax2", "Pax3", "Sox2", "Ascl1"), 
                 colors = colors2, null.color = "#DBDBDB", 
                 threshold = thresh, pt.size = 1, show.legend = T)
#dev.off()
#Fig.3C
genes <- c("Ccnd2", "Barhl1", "Cntn2", "Rbfox3", "Grin2b", "Gli1")
thresh <- c(3, 2, 1, 2, 2, 1)
names(thresh) <- genes
colors2 <- c(brewer.pal(10,'Paired')[c(9,1,3,5,7)], "red")

#devSVG("Fig.3C_WT_CGNP_markers.svg")
MultiFeaturePlot(WT, gene.list = genes, colors = colors2, threshold = thresh, pt.size = 1, null.color = "#DBDBDB")
#dev.off()
saveRDS(WT, "WT.rds")
```
#Projection of Vehicle Cells into WT tSNE
```{r}
#Figure 3D
genes.use <- intersect(WT@var.genes, rownames(Veh@data))
WT.loadings <- GetGeneLoadings(WT, 'pca', 1:14, genes.use = genes.use)
WT.embeddings <- GetCellEmbeddings(WT, 'pca', 1:14)
WT.tsne <- GetCellEmbeddings(WT, reduction.type = 'tsne', dims.use = 1:2)
WT@meta.data$ID <- rep("WT", nrow(WT@meta.data))
Veh@meta.data$ID <- Veh@meta.data$VehNode

data <- as.matrix(Veh@scale.data[genes.use,])
Veh.embeddings <- apply(WT.loadings, 2 , FUN = function(i) colSums(i*data))

train.tsne1 <- knnreg(WT.embeddings, WT.tsne[, 1], k = 5)
train.tsne2 <- knnreg(WT.embeddings, WT.tsne[, 2], k = 5)
test.tsne1 <- predict(train.tsne1, Veh.embeddings)
test.tsne2 <- predict(train.tsne2, Veh.embeddings)
test.tsne <- cbind(test.tsne1, test.tsne2)
rownames(test.tsne) <- rownames(Veh.embeddings)
colnames(test.tsne) <- paste0('tSNE_', 1:2)
Veh <- SetDimReduction(Veh, 'tsne', 'cell.embeddings', test.tsne)
colors2 <- c(brewer.pal(5, "Paired")[c(5, 1, 3)], 
             colors.use[c(15, 13, 12, 14, 16, 17)])
TSNEPlot(Veh, pt.size = 0.3, colors.use = colors2, 
         plot.order = rev(vehIDs))

Veh.tsne <- GetCellEmbeddings(Veh, 'tsne')
WT.tsne <- GetCellEmbeddings(WT, 'tsne')
M <- MergeSeurat(Veh, WT)
M <- SetDimReduction(M, 'tsne', 'cell.embeddings', rbind(Veh.tsne, WT.tsne))
M <- SetDimReduction(M, 'tsne', 'key', 'tSNE_')
M <- SetAllIdent(M, 'ID')

#devSVG("Fig.3D_VehCells_WT.knn.svg")
TSNEPlot(M, colors.use = c("#DBDBDB", colors2), 
         plot.order = rev(c("WT", vehIDs)),
         no.legend = F, pt.size = 0.5)
#dev.off()
```
#ICA-based analyses of CGNP-like Vehicle-treated cells
```{r}
knitr::opts_chunk$set(fig.width=9, fig.height=6) 
Veh <- readRDS('Veh.rds')
colors2 <- brewer.pal(9, "Paired")[c(5,1,3)]
Cent <- SubsetData(Veh, 
                   ident.use = grep("Node", levels(Veh@ident), value = T))
Cent@meta.data <- Cent@meta.data[WhichCells(Cent), ]
Cent@raw.data <- Cent@raw.data[, WhichCells(Cent)]
Cent@ident <- plyr::mapvalues(Cent@ident, levels(Cent@ident), 
                              c("Node A", "Node B", "Node C"))
Cent <- NormalizeData(Cent)
Cent <- FindVariableGenes(Cent, x.low.cutoff = 0.05, 
                         x.high.cutoff = 5, 
                         y.cutoff = 0.5, 
                         y.high.cutoff = Inf, 
                         num.bin = 40)
Cent <- RunICA(Cent, ics.compute = 4)
PrintICA(Cent, 1:4)
Cent <- RunTSNE(Cent, reduction.use = 'ica', dim.embed = 2, dims.use =1:4)
#devSVG("Fig.4A_ICA_tSNE_with_Nodes.svg")
TSNEPlot(Cent, colors.use = colors2)
#dev.off()

PrintICA(Cent, 4)
# Plot ICs, orient colors so "biological" genes are highlighted
# Fig. 4B
#devSVG("Fig.4B_IC1.svg")
FeaturePlot(Cent, 'IC1', cols.use = rev(magma(50)), pt.size = 1.5)
#dev.off()
#devSVG("Fig.4B_IC2.svg")
FeaturePlot(Cent, 'IC2', cols.use = magma(50), pt.size = 1.5)
#dev.off()
#devSVG("Fig.4B_IC3.svg")
FeaturePlot(Cent, 'IC3', cols.use = rev(magma(50)), pt.size = 1.5)
#dev.off()
#devSVG("Fig.4B_IC4.svg")
FeaturePlot(Cent, 'IC4', cols.use = rev(magma(50)), pt.size = 1.5)
#dev.off()

#Fig.4C
genes <- c("Ccnd1", "Ccne2", "Ccna2", "Ccnb2")
thresh <- c(2,1,2,2)
names(thresh) <- genes
colors2 <- brewer.pal(4,'Dark2')
#devSVG("Fig.4C_ICA_tSNE_with_Cyclins_and_arrows.svg")
MultiFeaturePlot(Cent, gene.list = genes, colors = colors2, 
                 threshold = thresh, pt.size = 1)
#dev.off()

# Fig.4E
Cent <- SetAllIdent(Cent, "VehNode")
genes <- c("Gli1", "Atoh1", "Mki67", "Pcna", "Ccnd1", "Ccnd2", 'Barhl1', "Rbfox3", "Cntn2", "Meg3")
#devSVG("Fig.4E_DotPlot.svg", width = 10)
DotPlot2(Cent, genes.plot = genes, 
         order = c("Node_A", "Node_B", "Node_C"), 
         plot.legend = T)
#dev.off()

# Seurat "Module Score" by cell cycle genes (Macosko, et al., 2015)
# Supplemental figure 1
ccg <- readLines("~/CellCycleGenes.txt")
g1s <- list(ccg[1:86])
s <- list(ccg[87:172])
g2m <- list(ccg[173:252])
m <- list(ccg[253:336])
mg1 <- list(ccg[337:381])
Cent <- AddModuleScore(object = Cent, genes.list = g1s, 
                       enrich.name = "G1S")
Cent <- AddModuleScore(object = Cent, genes.list = s,
                       enrich.name = "S")
Cent <- AddModuleScore(object = Cent, genes.list = g2m,
                       enrich.name = "G2M")
Cent <- AddModuleScore(object = Cent, genes.list = m, 
                       enrich.name = "M")
Cent <- AddModuleScore(object = Cent, genes.list = mg1,
                       enrich.name = "MG1")
ncol(Cent@meta.data)
colnames(Cent@meta.data) <- plyr::mapvalues(colnames(Cent@meta.data), 
                                            from = c("G1S1",
                                                     "S1",
                                                     "G2M1",
                                                     "M1",
                                                     "MG11"), 
                                            to = c("G1/S_Phase",
                                                   "S_Phase",
                                                   "G2/M_Phase",
                                                   "M_Phase",
                                                   "M/G1_Phase"))

p <- list()
p <- FeaturePlot(Cent, c("G1/S_Phase", "S_Phase", "G2/M_Phase", "M_Phase", "M/G1_Phase"), cols.use = magma(50), do.return = T)
genes <- c("Ccnd1", "Ccne2", "Ccna2", "Ccnb2")
thresh <- c(2,1,2,2)
names(thresh) <- genes
colors2 <- brewer.pal(4,'Dark2')
p[[6]] <- MultiFeaturePlot(Cent, gene.list = genes, colors = colors2, threshold = thresh, pt.size = 1)
#devSVG("Fig_S1.svg", width = 10, height = 15)
plot_grid(plotlist = p, ncol = 2)
#dev.off()

# Supplemental figure 2
genes <- c("Mki67", "Pcna", "Ccnd1", "Ccnd2", "Gli1", "Atoh1", "Barhl1", "Cntn2", "Rbfox3", "Meg3")
p <- list()
for(i in 1:10){
  message(genes[i])
  p[[i]] <- MultiFeaturePlot(Cent, genes[i], colors = colors.use[i], 
                             pt.size = 1, scale.color = T)
}
#devSVG("Fig_S2_Scaled.svg", width = 20, height = 11.25)
plot_grid(plotlist = p, ncol = 4)
#dev.off()
saveRDS(Cent, 'VehCent.rds')
```
##Add GO Annotations to ICAs
```{r}
library(xlsx)
IC.table <- read.xlsx("~/Supplemental_table_3.xlsx", 1)
ref.genes = Cent@var.genes

library(org.Mm.eg.db)
GO = toTable(org.Mm.egGO); SYMBOL = toTable(org.Mm.egSYMBOL)
GO_data_frame = data.frame(GO$go_id, GO$Evidence, 
                           SYMBOL$symbol[match(GO$gene_id, SYMBOL$gene_id)])

#create GOAllFrame object
library(AnnotationDbi)
GO_ALLFrame = GOAllFrame(GOFrame(GO_data_frame, organism = 'Mus musculus'))

#create gene set
library(GSEABase)
gsc <- GeneSetCollection(GO_ALLFrame, setType = GOCollection())

#perform GO enrichment analysis and save results to list - this make take several minutes
library(GOstats)
GSEAGO = vector('list',4)
for(i in seq(1, 12, by = 3)){
  GSEAGO[[i+1]] = summary(hyperGTest(GSEAGOHyperGParams(name = 'Mus musculus GO', 
              geneSetCollection = gsc, geneIds = as.character(IC.table[, i]), 
              universeGeneIds = ref.genes, ontology = 'BP', pvalueCutoff = 0.05, 
              conditional = FALSE, testDirection = 'over')))
  print(i)
}

for(i in seq(1, 12, by = 3)){
  write.xlsx(x = GSEAGO[[i+1]], file = 'Supp_Table3_GO.xlsx', sheetName = paste0('IC ', i), append = T)
}


cutoff.size = 100

GO.module.name = rep(NA,length(unique(modules)))
for (i in 1:length(unique(modules))){
  GO.module.name[i] = 
    GSEAGO[[i]][GSEAGO[[i]]$Size<cutoff.size,
    ][which(GSEAGO[[i]][GSEAGO[[i]]$Size<cutoff.size,]$Count==max(GSEAGO[[i]][GSEAGO[[i]]$
    Size<cutoff.size,]$Count)),7]
}

GO.module.name[1] = 'module 0'
#calculate module significance
MS.lscore = as.data.frame(cbind(GS.lscore,modules))
MS.lscore$log_p_value = -log10(as.numeric(MS.lscore$p_value))
MS.lscore = ddply(MS.lscore, .(modules), summarize, mean(log_p_value), sd(log_p_value))
colnames(MS.lscore) = c('modules','pval','sd')
MS.lscore.bar = as.numeric(MS.lscore[,2])
MS.lscore.bar[MS.lscore.bar<(-log10(0.05))] = 0
names(MS.lscore.bar) = GO.module.name

METree.GO = METree
label.order = match(METree$labels,paste0('ME',labels2colors(0:(length(unique(modules))-1))))
METree.GO$labels = GO.module.name[label.order]
plotTree.wBars(as.phylo(METree.GO), MS.lscore.bar, tip.labels = TRUE, scale = 0.2)
```

#Analysis of Sox2+ Cells in Vehicle-Tumor
```{r}
Veh <- readRDS("Veh.rds")
# Fig. 5A
#devSVG("Fig.5a_Sox2_YFP_Veh.svg")
MultiFeaturePlot(Veh, c("Sox2", "SmoM2-EYFP"), colors = c("red", "green"))
#dev.off()

# Fig. 5C
# Sox2+ Bar plot... it's a mess of code. Hang in there.
Veh <- SetAllIdent(Veh, "Replicate")
l <- list()
for(i in levels(Veh@ident)){
  l[[i]] <- SubsetData(Veh, ident.use = i)
}
classes <- c("Astrocytes",
             "Astrocytes YFP",
             "Oligodendrocytes",
             "Oligodendrocytes YFP",
             "Node A",
             "Node A YFP",
             "Node B",
             "Node B YFP",
             "Node C",
             "Node C YFP")
dat.raw <- data.frame(MB05 = rep(0, length(classes)),
                  MB06 = rep(0, length(classes)),
                  MB10 = rep(0, length(classes)),
                  MB13 = rep(0, length(classes)),
                  MB15 = rep(0, length(classes)))
popDat <- function(i){
o = l[[i]]
Sox2.cells <- colnames(o@data[, o@data["Sox2", ] > 0])
NodeA.cells <- intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Node_A"))
NodeB.cells <- intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Node_B"))
NodeC.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Node_C")))
Oligo.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Oligodendrocytes")))
Astro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Astrocytes")))
Endo.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Endothelial_Cells")))
Fibro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                 accept.value = "Vascular_Fibroblasts")))
Micro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Microglia")))
Neuro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "VehNode", 
                                    accept.value = "Neurons")))
YFP.cells <- intersect(Sox2.cells, 
                       colnames(o@data[, o@data["SmoM2-EYFP", ] > 0]))

#Add YFP
##RESTRICT TO ONLY CLASSES WITH > 10 CELLS
NodeA.yfp.cells <- intersect(NodeA.cells, YFP.cells)
#NodeA.cells <- NodeA.cells[!(NodeA.cells %in% YFP.cells)]
NodeB.yfp.cells <- intersect(NodeB.cells, YFP.cells)
#NodeB.cells <- NodeB.cells[!(NodeB.cells %in% YFP.cells)]
NodeC.yfp.cells <- intersect(NodeC.cells, YFP.cells)
#NodeC.cells <- NodeC.cells[!(NodeC.cells %in% YFP.cells)]
Oligo.yfp.cells <- intersect(Oligo.cells, YFP.cells)
#Oligo.cells <- Oligo.cells[!(Oligo.cells %in% YFP.cells)]
Astro.yfp.cells <- intersect(Astro.cells, YFP.cells)
#Astro.cells <- Astro.cells[!(Astro.cells %in% YFP.cells)]
#Endo.yfp.cells <- intersect(Endo.cells, YFP.cells)
#Endo.cells <- Endo.cells[!(Endo.cells %in% YFP.cells)]
#Fibro.yfp.cells <- intersect(Fibro.cells, YFP.cells)
#Fibro.cells <- Fibro.cells[!(Fibro.cells %in% YFP.cells)]
#Micro.yfp.cells <- intersect(Micro.cells, YFP.cells)
#Micro.cells <- Micro.cells[!(Micro.cells %in% YFP.cells)]
#Neuro.yfp.cells <- intersect(Neuro.cells, YFP.cells)
#Neuro.cells <- Neuro.cells[!(Neuro.cells %in% YFP.cells)]

s <- list(NodeA.cells,
          NodeA.yfp.cells,
          NodeB.cells,
          NodeB.yfp.cells,
          NodeC.cells,
          NodeC.yfp.cells,
          Oligo.cells,
          Oligo.yfp.cells,
          Astro.cells,
          Astro.yfp.cells)
p <- lapply(s, function(n) length(n))
dat.raw[, i] <- as.numeric(unlist(p))
}

dat <- sapply(names(l), function(i) popDat(i))
rownames(dat) <- classes
d <- dat[!(rownames(dat) %in% grep("YFP", rownames(dat), value = T)), ]
# Normalize by total cells by replicate
d <- apply(d, 2, function(i) i <- i/sum(i))
n <- data.frame(y = NA, ymin = NA, ymax = NA)
for(i in rownames(d)){
  n <- rbind(n, mean_se(d[i, ]))
}
n <- n[-1,]
d <- cbind(d, n)
d <- as.data.frame(d)
d$ID <- rownames(d)
d$yminA <- rep(0, nrow(d))
d$ymaxA <- rep(0, nrow(d))
for(r in 1:nrow(d)){
  d[r, "yminA"] <- sum(d[(r+1):5, "y"]) + d[r, "ymin"]
}
for(r in 1:nrow(d)){
  d[r, "ymaxA"] <- sum(d[(r+1):5, "y"]) + d[r, "ymax"]
}
d[5, "ymaxA"] <- d[5, "ymax"]
d[5, "yminA"] <- d[5, "ymin"]
d$ID <- factor(d$ID, levels = rownames(d))


levels(d$ID)
p <- list()
p[[1]] <- ggplot(d, aes(x = "Vehicle", y = y, fill = ID)) +
           geom_col(position = "fill") +
  scale_fill_manual(values = c(colors.use[c(12, 13)], 
                               brewer.pal(5, "Paired")[c(5, 1, 3)])) +
            geom_errorbar(data = d, 
                          aes(ymin = yminA, ymax = ymaxA, width = 0.3),
                          position = 'dodge')
#devSVG("Fig.5C_Sox2_StackBar.svg")
p[[1]]
#dev.off()

#write.xlsx(dat, "Sox2_Yfp_By_CellClass.xlsx")
```
### Sox2+ Cells Further Analysis (tSNE)
```{r}
# Fig 5D, 5E, 5F
Sox2.cells <- colnames(Veh@data[, Veh@data["Sox2", ] > 0])
S2 <- SubsetData(Veh, cells.use = Sox2.cells)
S2 <- FindVariableGenes(S2, x.low.cutoff = 0.05, 
                         x.high.cutoff = 5, 
                         y.cutoff = 0.75, 
                         y.high.cutoff = 10, 
                         num.bin = 40)
S2.pca <- TestPCA(S2, S2@var.genes, do.return = T)
S2 <- RunICA(S2, ic.genes = S2@var.genes, ics.compute = 4)
S2 <- RunTSNE(S2, 'ica', dims.use = c(1:4))
S2 <- SetAllIdent(S2, "VehNode")
TSNEPlot(S2, colors.use = colors.use)

# Fig 5D
#devSVG("Fig.5D_Sox2_Glial_Features.svg")
MultiFeaturePlot(S2, c("Aqp4", "Sox10"), 
                 colors = colors.use[c(12, 13)], pt.size = 1)
#dev.off()

# Fig 5E
Os <- WhichCells(S2, subset.name = "VehNode", 
                 accept.value = "Oligodendrocytes")
S2@meta.data$Highlight <- rep("low", nrow(S2@meta.data))
S2@meta.data[Os, 'Highlight'] <- "high"
S2 <- SetAllIdent(S2, "VehNode")
O <- SubsetData(S2, cells.use = Os)
TSNEPlot(O)
O@data <- O@misc[, WhichCells(O)]
p <- list()
p[[1]] <- MultiFeaturePlot(O, "Pdgfra", title = "Pdgfra", 
                           show.legend = F, pt.size = 1)
p[[2]] <- MultiFeaturePlot(O, "Mbp", title = "Mbp",
                           show.legend = F, pt.size = 1)
p[[3]] <- MultiFeaturePlot(O, "Plp1", title = "Plp1", 
                           show.legend = F, pt.size = 1)
p[[4]] <- MultiFeaturePlot(O, "Mog", title = "Mog", 
                           show.legend = F, pt.size = 1)
p[[5]] <- MultiFeaturePlot(O, "SmoM2-EYFP", title = "Yfp", 
                           show.legend = F, pt.size = 1)
S2 <- SetAllIdent(S2, "Highlight")
p[[6]] <- TSNEPlot(S2, colors.use = c(colors.use[13], grey(0.7)), 
                   plot.title = "Oligodendrocytes", no.legend = T, 
                   do.return = T)
#devSVG("Fig.5E_Composite_Features_Sox2+Oligos.svg")
plot_grid(p[[6]], p[[1]],
          p[[2]], p[[3]],
          p[[4]], p[[5]], ncol = 2)
#dev.off()

# Chi Square testing on Mbp, Mog, Pdgfra, SmoM2-EYFP in Oligos
OPC <- TSNEPlot(O, do.identify = T)
Mat <- TSNEPlot(O, do.identify = T)

# Function to make 2x2 matrix - group x pos/neg for gene
getSum <- function(i, O, cells1, cells2){
  pos1 <- sum(O@data[i, cells1] > 0)
  neg1 <- length(O@data[i, cells1]) - pos1
  pos2 <- sum(O@data[i, cells2] > 0)
  neg2 <- length(O@data[i, cells2]) - pos2
  mtx <- data.frame("cells1" = c(pos1, neg1), 
                    "cells2" = c(pos2, neg2))
  rownames(mtx) <- c("Pos", "Neg")
  return(mtx)
}
genes <- c("Mbp", "Mog", "Pdgfra", "SmoM2-EYFP")
for(gene in genes){
  print(gene)
  print(chisq.test(getSum(gene, O, OPC, Mat))$p.value)
}
"Mbp"
[1] 1.085564e-17
[1] "Mog"
[1] 9.160045e-07
[1] "Pdgfra"
[1] 1.293513e-20
[1] "SmoM2-EYFP"
[1] 0.5071907

# Fig 5E
As <- WhichCells(S2, subset.name = "VehNode", 
                 accept.value = "Astrocytes")
S2@meta.data$Highlight <- rep("low", nrow(S2@meta.data))
S2@meta.data[As, 'Highlight'] <- "high"

S2 <- SetAllIdent(S2, "VehNode")
A <- SubsetData(S2, cells.use = As)
TSNEPlot(A)
A@data <- A@misc[, WhichCells(A)]
p <- list()
p[[1]] <- MultiFeaturePlot(A, "Olig1", title = "Olig1", 
                           show.legend = F, pt.size = 3)
p[[2]] <- MultiFeaturePlot(A, "SmoM2-EYFP", title = "Yfp",
                           show.legend = F, pt.size = 1)
S2 <- SetAllIdent(S2, "Highlight")
p[[3]] <- TSNEPlot(S2, colors.use = c(colors.use[12], grey(0.7)), 
                   plot.title = "Astrocytes", no.legend = T, 
                   do.return = T)
#devSVG("Fig.5E_Composite_Features_Sox2+Astros.svg", width = 3.5)
plot_grid(p[[3]],
          p[[1]],
          p[[2]], ncol = 1)
#dev.off()
AP <- TSNEPlot(A, do.identify = T)
AMat <- TSNEPlot(A, do.identify = T)
genes <- c("Olig1", "SmoM2-EYFP")
for(gene in genes){
  print(gene)
  print(chisq.test(getSum(gene, A, AP, AMat))$p.value)
}
[1] "Olig1"
[1] 2.741437e-08
[1] "SmoM2-EYFP"
[1] 0.01773535

```
#Analysis of Treated and Untreated Grouped Together (GT)
```{r}
GT <- readRDS('GT.rds')
#Separate into control & treatment sets for plotting
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
# Investigate Stromal Markers
# Fig. 6A
genes <- c("Col3a1", "C1qb", "Meg3", "Sox10", 'Aqp4', "Pecam1")
thresh <- c(3,3,4,1,3,2)
names(thresh) <- genes
colors2 <- colors.use[c(16, 14, 15, 13, 12, 17)]
#devSVG("Fig.6A_GT_Stromal_Markers_GT.svg")
MultiFeaturePlot(GT, gene.list = genes, colors = colors2, 
                 threshold = thresh)
#dev.off()
#devSVG("Fig.6A_GT_Stromal_Markers_Ct.svg")
MultiFeaturePlot(Ct, gene.list = genes, colors = colors2,
                 threshold = thresh)
#dev.off()
#devSVG("Fig.6A_GT_Stromal_Markers_Tr.svg")
MultiFeaturePlot(Tr, gene.list = genes, colors = colors2,
                 threshold = thresh)
#dev.off()
```
###Node-level analyses
```{r}
# To better organize we want to isolate the solid tumor from the stroma
# Exact same process as in vehicle-alone above
# Fig. 6B
GT <- SetAllIdent(GT, 'GTClust')
#devSVG("Fig.6B_GT_HCA_Dendrogram.svg")
GT <- BuildClusterTree(GT, pcs.use = 1:10)
#dev.off()
TSNEPlot(GT, colors.use = colors.use)
# Fig 6B
GT@ident <- plyr::mapvalues(GT@ident, from = levels(GT@ident), 
                             to = c("Node_B", "Node_B", "Node_A", 
                                    "Node_A", "Node_A", "Node_C",
                                    "Node_C", "Node_C", "Node_D",
                                    "Node_D","Node_D",
                                    "Astrocytes", "Oligodendrocytes",
                                    "Microglia", "Neurons",
                                    "Vascular_Fibroblasts",
                                    "Endothelial_Cells"))
GT <- StashIdent(GT, "GTNode")
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
gtIDs <- c("Node_A", "Node_B", "Node_C", "Node_D", "Neurons",
           "Oligodendrocytes", "Astrocytes", "Microglia",
           "Vascular_Fibroblasts", "Endothelial_Cells")
colors2 <- colors.use[c(1:4, 15, 13, 12, 14, 16, 17)]
#devSVG("Fig.6B_GT_Nodes_on_t-SNE_GT.svg")
TSNEPlot(GT, colors.use = colors2, plot.order = rev(gtIDs),
         do.return = T, pt.size = 0.5)
#dev.off()
#devSVG("Fig.6B_GT_Nodes_on_t-SNE_Ct.svg")
TSNEPlot(Ct, colors.use = colors2, plot.order = rev(gtIDs),
         do.return = T, pt.size = 0.5)
#dev.off()
#devSVG("Fig.6B_GT_Nodes_on_t-SNE_Tr.svg")
TSNEPlot(Tr, colors.use = colors2, plot.order = rev(gtIDs),
         do.return = T, pt.size = 0.5)
#dev.off()

# Fig 6C
GT.cent <-  SubsetData(GT, subset.name = 'GTNode',
                       accept.value = c("Node_A", "Node_B",
                                        "Node_C", "Node_D"))
genes <- c("Gli1", "Atoh1", "Mki67", "Pcna", "Ccnd1", "Ccnd2", 
           'Barhl1', "Rbfox3", "Cntn2", "Meg3")
#devSVG("Fig.6C_GT_DotPlot.svg", width = 10)
DotPlot2(GT.cent, genes.plot = genes, 
         order = c("Node_A", "Node_B", "Node_C", "Node_D"),
         plot.legend = T)
#dev.off()
# Fig 6D
#devSVG("Fig.6A_GT_Stromal_Markers_GT.svg")
MultiFeaturePlot(GT, "SmoM2-EYFP")
#dev.off()
#devSVG("Fig.6A_GT_Stromal_Markers_GT.svg")
MultiFeaturePlot(Ct, "SmoM2-EYFP")
#dev.off()
#devSVG("Fig.6A_GT_Stromal_Markers_GT.svg")
MultiFeaturePlot(Tr, "SmoM2-EYFP")
#dev.off()
saveRDS(GT, "GT.rds")
```
#Projection of GT Cells into WT tSNE
```{r}
#Figure 3D
genes.use <- intersect(WT@var.genes, rownames(GT@data))
WT.loadings <- GetGeneLoadings(WT, 'pca', 1:14, genes.use = genes.use)
WT.embeddings <- GetCellEmbeddings(WT, 'pca', 1:14)
WT.tsne <- GetCellEmbeddings(WT, reduction.type = 'tsne', dims.use = 1:2)
WT@meta.data$ID <- rep("WT", nrow(WT@meta.data))
GT@meta.data$ID <- GT@meta.data$GTNode

data <- as.matrix(GT@scale.data[genes.use,])
GT.embeddings <- apply(WT.loadings, 2 , 
                       FUN = function(i) colSums(i*data))

train.tsne1 <- knnreg(WT.embeddings, WT.tsne[, 1], k = 5)
train.tsne2 <- knnreg(WT.embeddings, WT.tsne[, 2], k = 5)
test.tsne1 <- predict(train.tsne1, GT.embeddings)
test.tsne2 <- predict(train.tsne2, GT.embeddings)
test.tsne <- cbind(test.tsne1, test.tsne2)
rownames(test.tsne) <- rownames(GT.embeddings)
colnames(test.tsne) <- paste0('tSNE_', 1:2)
GT <- SetDimReduction(GT, 'tsne', 'cell.embeddings', test.tsne)
colors2 <- colors.use[c(2, 1, 3:4, 15, 13, 12, 14, 16, 17)]
TSNEPlot(GT, pt.size = 0.3, colors.use = colors2, 
         plot.order = rev(gtIDs))
# Plot Control cells in projection
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Ct.tsne <- GetCellEmbeddings(Ct, 'tsne')
WT.tsne <- GetCellEmbeddings(WT, 'tsne')
M <- MergeSeurat(Ct, WT)
M <- SetDimReduction(M, 'tsne', 'cell.embeddings', 
                     rbind(Ct.tsne, WT.tsne))
M <- SetDimReduction(M, 'tsne', 'key', 'tSNE_')
M <- SetAllIdent(M, 'ID')
#devSVG("Fig.6E_GTCells_WT_Ct.knn.svg")
TSNEPlot(M, colors.use = c("#DBDBDB", colors2), 
         plot.order = rev(c("WT", gtIDs)),
         no.legend = F, pt.size = 0.5)
#dev.off()
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
Tr.tsne <- GetCellEmbeddings(Tr, 'tsne')
WT.tsne <- GetCellEmbeddings(WT, 'tsne')
M1 <- MergeSeurat(Tr, WT)
M1 <- SetDimReduction(M1, 'tsne', 'cell.embeddings', 
                     rbind(Tr.tsne, WT.tsne))
M1 <- SetDimReduction(M1, 'tsne', 'key', 'tSNE_')
M1 <- SetAllIdent(M1, 'ID')
#devSVG("Fig.6E_GTCells_WT_Tr.knn.svg")
TSNEPlot(M1, colors.use = c("#DBDBDB", colors2), 
         plot.order = rev(c("WT", gtIDs)),
         no.legend = F, pt.size = 0.5)
#dev.off()
```
#ICA-based analyses of CGNP-like Grouped-treatment cells
```{r}
# Fig 6F
GT <- readRDS("GT.rds")
GT <- SetAllIdent(GT, "GTNode")
Cent <- SubsetData(GT, 
                   ident.use = grep("Node", levels(GT@ident), value = T))
Cent@meta.data <- Cent@meta.data[WhichCells(Cent), ]
Cent@raw.data <- Cent@raw.data[, WhichCells(Cent)]
Cent <- NormalizeData(Cent)
Cent <- FindVariableGenes(Cent, x.low.cutoff = 0.05, 
                         x.high.cutoff = 5, 
                         y.cutoff = 0.5, 
                         y.high.cutoff = Inf, 
                         num.bin = 40)
Cent <- RunICA(Cent, ics.compute = 4)
PrintICA(Cent, 1:4)
Cent <- RunTSNE(Cent, reduction.use = 'ica', 
                dim.embed = 2, dims.use =1:4)
TSNEPlot(Cent, colors.use = colors.use)
PrintICA(Cent, 1)
# Plot Treatment and control-separated by the differentiation IC
# Fig. 4B
#devSVG("Fig.6F_IC1_Ct.svg")
FeaturePlot(Cent, 'IC1', cols.use = magma(50), pt.size = 1.5, 
            cells.use = WhichCells(Cent, subset.name = "Treatment",
                                   accept.value = "Vehicle"))
#dev.off()
#devSVG("Fig.4B_IC2_Tr.svg")
FeaturePlot(Cent, 'IC1', cols.use = magma(50), pt.size = 1.5, 
            cells.use = WhichCells(Cent, subset.name = "Treatment",
                                   accept.value = "Vismodegib"))
#dev.off()
saveRDS(Cent, 'GTCent.rds')
```
#Differential population distribution plots
```{r}
# Fig 6G
# Test significance
aovTable(GT, alternate.plot = F, do.plot = F, 
         run.test = T, level.dep = "GTNode", level.ind = "Treatment")
# Draw Plot
#devSVG("Fig.6G.svg", width = 10)
aovTable(GT, alternate.plot = T, do.plot = F, 
         run.test = F, level.dep = "GTNode", level.ind = "Treatment")
#dev.off()
# Fig 6H
# Find what fraction of total YFP cells are in each cluster, by replicate
YFP <- SubsetData(GT, 
                  cells.use = names(which(GT@data["SmoM2-EYFP", ] > 0)))
YFP <- SetAllIdent(YFP, "GTNode")
# Get Significance
aovTable(YFP, alternate.plot = F, do.plot = F, 
         run.test = T, level.dep = "GTNode", level.ind = "Treatment")
# Draw Plot
#devSVG("Fig.6H_YFP_Fractions.svg", width = 10)
aovTable(YFP, alternate.plot = T, do.plot = F, 
         run.test = F, level.dep = "GTNode", level.ind = "Treatment")

#dev.off()
```
#Drug resistant sub-populations
```{r}
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
#devSVG("Fig.7A_Gli1_Ctrl.cells.svg")
MultiFeaturePlot(Ct, "Gli1")
#dev.off()
#devSVG("Fig.7A_Gli1_Drug.cells.svg")
MultiFeaturePlot(Tr, "Gli1")
#dev.off()
#devSVG("Fig.7C_Gli1+Hes1_Ctrl.cells.svg")
MultiFeaturePlot(Ct, c("Gli1", "Hes1"))
#dev.off()
#devSVG("Fig.7C_Gli1+Hes1_Drug.cells.svg")
MultiFeaturePlot(Tr, c("Gli1", "Hes1"))
#dev.off()
#devSVG("Fig.7E_Gli1+Myod1_Ctrl.cells.svg")
MultiFeaturePlot(Ct, c("Gli1", "Myod1"), colors = colors.use[c(1,3)])
#dev.off()
#devSVG("Fig.7E_Gli1+Myod1_Drug.cells.svg")
MultiFeaturePlot(Tr, c("Gli1", "Myod1"), colors = colors.use[c(1,3)])
#dev.off()

# Fig 8A

#devSVG("Fig.8A_Ezh2_Ctrl.cells.svg")
MultiFeaturePlot(Ct, "Ezh2", colors = colors.use[5])
#dev.off()
#devSVG("Fig.8A_Ezh2_Drug.cells.svg")
MultiFeaturePlot(Tr, "Ezh2", colors = colors.use[5])
#dev.off()
#devSVG("Fig.8A_Suz12_Ctrl.cells.svg")
MultiFeaturePlot(Ct, "Suz12", colors = colors.use[2])
#dev.off()
#devSVG("Fig.8A_Suz12_Drug.cells.svg")
MultiFeaturePlot(Tr, "Suz12", colors = colors.use[2])
#dev.off()
#devSVG("Fig.8A_Eed_Ctrl.cells.svg")
MultiFeaturePlot(Ct, "Eed", colors = colors.use[3])
#dev.off()
#devSVG("Fig.8A_Eed_Drug.cells.svg")
MultiFeaturePlot(Tr, "Eed", colors = colors.use[3])
#dev.off()
#devSVG("Fig.8A_FullPRC2_Ctrl.cells.svg")
MultiFeaturePlot(Ct, c("Ezh2", "Suz12", "Eed"),
                 plot.intersection = T, pct.cutoff = 1, 
                 colors = colors.use[4], multi.label = 'PRC2')
#dev.off()
#devSVG("Fig.8A_FullPRC2_Drug.cells.svg")
MultiFeaturePlot(Tr, c("Ezh2", "Suz12", "Eed"),
                 plot.intersection = T, pct.cutoff = 1, 
                 colors = colors.use[4], multi.label = 'PRC2')
#dev.off()
```

#Gene-Gene Correlation with MAGIC
```{r}
# Fig 8B, 8C
library(Rmagic)
#install.magic()
GT <- readRDS("GT.rds")
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
Veh_M <- as.data.frame(Rmagic::magic(t(Ct@data), 
                                         genes=c("Gli1", 
                                                 "Sufu", 
                                                 "Ptch1"), 
                                         t=12))
Vis_M <- as.data.frame(Rmagic::magic(t(Tr@data), 
                                         genes=c("Gli1", 
                                                 "Sufu", 
                                                 "Ptch1"), 
                                         t=12))
Veh.meta <- as.data.frame(Ct@meta.data)
Vis.meta <- as.data.frame(Tr@meta.data)

Veh_label <- merge(Veh.meta, Veh_M, by=0, all=T, row.names = rownames(Veh.meta))
Vis_label <- merge(Vis.meta, Vis_M, by=0, all=T, row.names = rownames(Vis.meta))

Veh_Node_label <- subset(Veh_label, ID == 'Node A' |ID == 'Node B' | ID =='Node C')
Vis_Node_label <- subset(Vis_label, ID == 'Node A' |ID == 'Node B' | ID =='Node C')



dat <- Veh_label
tests <- Veh_label[, "Gli1"]
reps <- Veh_label[, "Replicate"]
counts.mtx <- matrix(rep('0'), 
                     ncol = length(tests),
                     nrow = length(reps),
                     dimnames = list(reps, tests))
getCounts <- function(b){
    r <- which(dat[, "Replicate"] == b)
    d <- r[, "Gli1"]
    return(d)
}
  counts.mtx <- t(sapply(reps, 
                         function(b) counts.mtx[b, ] = getCounts(b)))

  treatment <- sapply(reps, function(i) unique(dat[which(dat[, rep.name] == i), level.ind]))
  counts.mtx <- as.data.frame(cbind(counts.mtx, 'Treatment' = as.character(treatment)))
  counts.mtx[, 1:length(tests)] <- apply(counts.mtx[, 1:length(tests)], 2, function(x) as.numeric(as.character(x)))
  if(run.test){
    t <- sapply(X = colnames(counts.mtx)[1:length(tests)], 
                FUN = function(i) summary(aov(as.formula(paste0(i, ' ~ Treatment')), data = counts.mtx)))
   return(t) 
  }









p <- list()
p[[1]] <- ggplot(data = Veh_Node_label, aes(x = Gli1, y = Ptch1, color = ID)) +
  geom_point() + 
  geom_smooth(method = 'lm', formula = y~x, color = "black") + 
  scale_color_manual(values = colors.use, guide = F) +
  xlim(0,0.4) +
  ylim(0,0.105)
p[[2]] <- ggplot(data = Vis_Node_label, aes(x = Gli1, y = Ptch1, color = ID)) +
  geom_point() + 
  geom_smooth(method = 'lm', formula = y~x, color = "black") + 
  scale_color_manual(values = colors.use, guide = F) +
  xlim(0,0.4) +
  ylim(0,0.105)
p[[3]] <- ggplot(data = Veh_Node_label, aes(x = Sufu, y = Gli1, color = ID)) +
  geom_point() + 
  geom_smooth(method = 'lm', formula = y~x, color = "black") + 
  scale_color_manual(values = colors.use, guide = F) +
  xlim(0.05,0.205) +
  ylim(0,0.4)
p[[4]] <- ggplot(data = Vis_Node_label, aes(x = Sufu, y = Gli1, color = ID)) +
  geom_point() + 
  geom_smooth(method = 'lm', formula = y~x, color = "black") + 
  scale_color_manual(values = colors.use, guide = F) +
  xlim(0.05,0.205) +
  ylim(0,0.4)
devSVG("Fig.8B_8C_Correlation_Plots_Supplement.svg")
plot_grid(p[[1]], p[[2]],
          p[[3]], p[[4]], ncol = 2)
dev.off()











```

# Sox2+ ICA tSNE - Grouped Treatment
```{r}
# Fig 5D, 5E, 5F
Sox2.cells <- colnames(GT@data[, GT@data["Sox2", ] > 0])
S2 <- SubsetData(GT, cells.use = Sox2.cells)
S2 <- FindVariableGenes(S2, x.low.cutoff = 0.05, 
                         x.high.cutoff = 5, 
                         y.cutoff = 0.75, 
                         y.high.cutoff = 10, 
                         num.bin = 40)
S2.pca <- TestPCA(S2, S2@var.genes, do.return = T)
S2 <- RunICA(S2, ic.genes = S2@var.genes, ics.compute = 4)
S2 <- RunTSNE(S2, 'ica', dims.use = c(1:4))
S2 <- SetAllIdent(S2, "GTNode")
TSNEPlot(S2, colors.use = colors.use)
S2.Ct <- SubsetData(S2, subset.name = "Treatment", 
                    accept.value = "Vehicle")
S2.Tr <- SubsetData(S2, subset.name = "Treatment", 
                    accept.value = "Vismodegib")
S2.Ct <- SetAllIdent(S2.Ct, "Treatment")
S2.Tr <- SetAllIdent(S2.Tr, "Treatment")
# Fig 8D
#devSVG("Fig.8D_Sox2_Depletion_Ctrl.svg")
MultiFeaturePlot(S2.Ct, c("Fabp7", "Hes1"), 
                 colors = colors.use, pt.size = 1)
#dev.off()
#devSVG("Fig.8D_Sox2_Depletion_Drug.svg")
MultiFeaturePlot(S2.Tr, c("Fabp7", "Hes1"), 
                 colors = colors.use, pt.size = 1)
#dev.off()

# Fig 8E
p <- TSNEPlot(S2.Ct, pt.size = 1, no.legend = T,
              do.return = T)
frame <- RunFrame(Object = S2.Ct, gene.use = "Nes")
p <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status))
frame <- RunFrame(Object = S2.Ct, gene.use = "Vim", threshold = 3)
p <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status))
frame <- RunFrame(Object = S2.Ct, gene.use = "SmoM2-EYFP")
p2 <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status), size = 1) +
      scale_colour_manual(values = c("red",
                                     "green",
                                     grey(0.7),
                                     "purple"), guide = F)
#devSVG("Fig.8E_Sox2_Depletion_Ctrl.svg")
p2
#dev.off()


p <- TSNEPlot(S2.Tr, pt.size = 1, no.legend = T,
              do.return = T)
frame <- RunFrame(Object = S2.Tr, gene.use = "Nes")
p <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status))
frame <- RunFrame(Object = S2.Tr, gene.use = "Vim", threshold = 3)
p <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status))
frame <- RunFrame(Object = S2.Tr, gene.use = "SmoM2-EYFP")
p2 <- p +  geom_point(data = frame[which(frame$Plot.Status != "None"), ], 
                aes(x = tSNE_1, y = tSNE_2, color = Plot.Status), size = 1) +
      scale_colour_manual(values = c("red",
                                     "green",
                                     "purple",
                                      grey(0.7)), guide = F)
#devSVG("Fig.8E_Sox2_Depletion_Drug.svg")
p2
#dev.off()
```

#Vismo-Treated Sox2+ Bar Figure
```{r}
# Sox2+ Bar plot... it's way more of a mess of code now!
# Keep hanging in there.
Ct <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vehicle")
Tr <- SubsetData(GT, subset.name = "Treatment", 
                 accept.value = "Vismodegib")
Ct <- SetAllIdent(Ct, "Replicate")
l <- list()
for(i in levels(Ct@ident)){
  l[[i]] <- SubsetData(Ct, ident.use = i)
}
classes <- c("Astrocytes",
             "Astrocytes YFP",
             "Oligodendrocytes",
             "Oligodendrocytes YFP",
             "Node A",
             "Node A YFP",
             "Node B",
             "Node B YFP",
             "Node C",
             "Node C YFP",
             "Node D",
             "Node D YFP")
dat.raw <- data.frame(MB05 = rep(0, length(classes)),
                  MB06 = rep(0, length(classes)),
                  MB10 = rep(0, length(classes)),
                  MB13 = rep(0, length(classes)),
                  MB15 = rep(0, length(classes)))
popDat <- function(i){
o = l[[i]]
Sox2.cells <- colnames(o@data[, o@data["Sox2", ] > 0])
NodeA.cells <- intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Node_A"))
NodeB.cells <- intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Node_B"))
NodeC.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Node_C")))
NodeD.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Node_D")))
Oligo.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Oligodendrocytes")))
Astro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Astrocytes")))
Endo.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Endothelial_Cells")))
Fibro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                 accept.value = "Vascular_Fibroblasts")))
Micro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Microglia")))
Neuro.cells <- intersect(Sox2.cells, intersect(Sox2.cells, 
                         WhichCells(o, subset.name = "GTNode", 
                                    accept.value = "Neurons")))
YFP.cells <- intersect(Sox2.cells, 
                       colnames(o@data[, o@data["SmoM2-EYFP", ] > 0]))

#Add YFP
##RESTRICT TO ONLY CLASSES WITH > 10 CELLS
NodeA.yfp.cells <- intersect(NodeA.cells, YFP.cells)
#NodeA.cells <- NodeA.cells[!(NodeA.cells %in% YFP.cells)]
NodeB.yfp.cells <- intersect(NodeB.cells, YFP.cells)
#NodeB.cells <- NodeB.cells[!(NodeB.cells %in% YFP.cells)]
NodeC.yfp.cells <- intersect(NodeC.cells, YFP.cells)
#NodeC.cells <- NodeC.cells[!(NodeC.cells %in% YFP.cells)]
NodeD.yfp.cells <- intersect(NodeD.cells, YFP.cells)
#NodeD.cells <- NodeD.cells[!(NodeD.cells %in% YFP.cells)]
Oligo.yfp.cells <- intersect(Oligo.cells, YFP.cells)
#Oligo.cells <- Oligo.cells[!(Oligo.cells %in% YFP.cells)]
Astro.yfp.cells <- intersect(Astro.cells, YFP.cells)
#Astro.cells <- Astro.cells[!(Astro.cells %in% YFP.cells)]
#Endo.yfp.cells <- intersect(Endo.cells, YFP.cells)
#Endo.cells <- Endo.cells[!(Endo.cells %in% YFP.cells)]
#Fibro.yfp.cells <- intersect(Fibro.cells, YFP.cells)
#Fibro.cells <- Fibro.cells[!(Fibro.cells %in% YFP.cells)]
#Micro.yfp.cells <- intersect(Micro.cells, YFP.cells)
#Micro.cells <- Micro.cells[!(Micro.cells %in% YFP.cells)]
#Neuro.yfp.cells <- intersect(Neuro.cells, YFP.cells)
#Neuro.cells <- Neuro.cells[!(Neuro.cells %in% YFP.cells)]

s <- list(NodeA.cells,
          NodeA.yfp.cells,
          NodeB.cells,
          NodeB.yfp.cells,
          NodeC.cells,
          NodeC.yfp.cells,
          NodeD.cells,
          NodeD.yfp.cells,
          Oligo.cells,
          Oligo.yfp.cells,
          Astro.cells,
          Astro.yfp.cells)
p <- lapply(s, function(n) length(n))
dat.raw[, i] <- as.numeric(unlist(p))
}

dat <- sapply(names(l), function(i) popDat(i))
rownames(dat) <- classes
d <- dat[!(rownames(dat) %in% grep("YFP", rownames(dat), value = T)), ]
# Normalize by total cells by replicate
d <- apply(d, 2, function(i) i <- i/sum(i))
n <- data.frame(y = NA, ymin = NA, ymax = NA)
for(i in rownames(d)){
  n <- rbind(n, mean_se(d[i, ]))
}
n <- n[-1,]
d <- cbind(d, n)
d <- as.data.frame(d)
d$ID <- rownames(d)
d$yminA <- rep(0, nrow(d))
d$ymaxA <- rep(0, nrow(d))
for(r in 1:nrow(d)){
  d[r, "yminA"] <- sum(d[(r+1):6, "y"]) + d[r, "ymin"]
}
for(r in 1:nrow(d)){
  d[r, "ymaxA"] <- sum(d[(r+1):6, "y"]) + d[r, "ymax"]
}
d[6, "ymaxA"] <- d[6, "ymax"]
d[6, "yminA"] <- d[6, "ymin"]
d$ID <- factor(d$ID, levels = rownames(d))


levels(d$ID)
p <- list()
p[[1]] <- ggplot(d, aes(x = "Vehicle", y = y, fill = ID)) +
           geom_col(position = "fill") +
  scale_fill_manual(values = c(colors.use[c(12, 13)], 
                               colors.use[1:4])) +
            geom_errorbar(data = d, 
                          aes(ymin = yminA, ymax = ymaxA, width = 0.3),
                          position = 'dodge')
#devSVG("Fig.8F_Sox2_StackBar_VehCells.svg")
p[[1]]
#dev.off()

#write.xlsx(dat, "Sox2_Yfp_GT_VehCells.xlsx")

Tr <- SetAllIdent(Tr, "Replicate")
l <- list()
for(i in levels(Tr@ident)){
  l[[i]] <- SubsetData(Tr, ident.use = i)
}
classes <- c("Astrocytes",
             "Astrocytes YFP",
             "Oligodendrocytes",
             "Oligodendrocytes YFP",
             "Node A",
             "Node A YFP",
             "Node B",
             "Node B YFP",
             "Node C",
             "Node C YFP",
             "Node D",
             "Node D YFP")
dat.raw <- data.frame(MB04 = rep(0, length(classes)),
                  MB07 = rep(0, length(classes)),
                  MB09 = rep(0, length(classes)),
                  MB12 = rep(0, length(classes)),
                  MB14 = rep(0, length(classes)))
dat <- sapply(names(l), function(i) popDat(i))
rownames(dat) <- classes
d <- dat[!(rownames(dat) %in% grep("YFP", rownames(dat), value = T)), ]
# Normalize by total cells by replicate
d <- apply(d, 2, function(i) i <- i/sum(i))
n <- data.frame(y = NA, ymin = NA, ymax = NA)
for(i in rownames(d)){
  n <- rbind(n, mean_se(d[i, ]))
}
n <- n[-1,]
d <- cbind(d, n)
d <- as.data.frame(d)
d$ID <- rownames(d)
d$yminA <- rep(0, nrow(d))
d$ymaxA <- rep(0, nrow(d))
for(r in 1:nrow(d)){
  d[r, "yminA"] <- sum(d[(r+1):6, "y"]) + d[r, "ymin"]
}
for(r in 1:nrow(d)){
  d[r, "ymaxA"] <- sum(d[(r+1):6, "y"]) + d[r, "ymax"]
}
d[6, "ymaxA"] <- d[6, "ymax"]
d[6, "yminA"] <- d[6, "ymin"]
d$ID <- factor(d$ID, levels = rownames(d))


levels(d$ID)
p <- list()
p[[1]] <- ggplot(d, aes(x = "Vehicle", y = y, fill = ID)) +
           geom_col(position = "fill") +
  scale_fill_manual(values = c(colors.use[c(12, 13)], 
                               colors.use[1:4])) +
            geom_errorbar(data = d, 
                          aes(ymin = yminA, ymax = ymaxA, width = 0.3),
                          position = 'dodge')
#devSVG("Fig.8F_Sox2_StackBar_VisCells.svg")
p[[1]]
#dev.off()

#write.xlsx(dat, "Sox2_Yfp_GT_VisCells.xlsx")
```

#Surface Differentiation (Neoantigen)
```{r}
source("~/SingleCell.Utilities.R")
GT <- readRDS("~/GT.rds")
atlas <- read.xlsx(file = "~/S1_File.xlsx", sheetIndex = 1)
head(atlas)
mGenes <- as.character(unique(atlas[grep("MOUSE", atlas$UP_entry_name), "ENTREZ.gene.symbol"]))
mGenes
#groups: A/B, A/B/C, A/B/C/D (Veh_only) x w or w/o glia
#Node A/B w/wo glia
#
GT <- SetAllIdent(GT, "ID")
markers <- FindMarkers(GT, ident.1 = c("Node A", "Node B"), test.use = "t", 
                       min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "AB-_Intersect.xlsx")
markers1 <- markers
#Node A/B w/ glia
#
markers <- FindMarkers(GT, ident.1 = c("Node A", "Node B", "Astrocytes", "Oligodendrocytes"),
                       test.use = "t", min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "AB+_Intersect.xlsx")
markers2 <- markers
#Node A/B/C w/o glia 
#
markers <- FindMarkers(GT, ident.1 = c("Node A", "Node B", "Node C"), test.use = "t", 
                       min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "ABC-_Intersect.xlsx")
markers3 <- markers
#Node A/B/C w/ glia
#
markers <- FindMarkers(GT, ident.1 = c("Node A", "Node B", "Node C",
                                       "Astrocytes", "Oligodendrocytes"),
                       test.use = "t", min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "ABC+_Intersect.xlsx")
markers4 <- markers
#Veh Node A/B/C/D w/o glia
#
Veh <- SubsetData(GT, subset.name = "Treatment", accept.value = "Vehicle")
markers <- FindMarkers(Veh, ident.1 = c("Node A", "Node B", "Node C", "Node D"),
                       test.use = "t", min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "ABCD-_Veh_Intersect.xlsx")
markers5 <- markers
#Veh Node A/B/C/D w/ glia
#
markers <- FindMarkers(Veh, ident.1 = c("Node A", "Node B", "Node C", "Node D",
                                       "Astrocytes", "Oligodendrocytes"),
                       test.use = "t", min.diff.pct = 0.1, min.pct = 0, only.pos = T)
markers <- markers[intersect(rownames(markers), mGenes), ]
write.xlsx(markers, "ABCD+_Veh_Intersect.xlsx")
markers6 <- markers
q()
xls <- c("AB-_Intersect.xlsx", "ABC-_Intersect.xlsx", "ABCD-_Veh_Intersect.xlsx",
         "AB+_Intersect.xlsx", "ABC+_Intersect.xlsx", "ABCD+_Veh_Intersect.xlsx")
g <- character()
for(xl in xls){
  g <- c(g, as.character(read.xlsx(paste0(xl), sheetIndex=1)[, 1]))
}
g <- unique(g)
g

for(gene in g){
pdf(paste0("~/Neoantigens/", gene, ".pdf"))
print(MultiFeaturePlot(GT, gene))
dev.off()
}


pdf("Slc29a1.pdf")
MultiFeaturePlot(GT, "Slc29a1")
dev.off()
```
#Cell Cycle Regression
```{r}
# In R 3.6.0
source("~/SingleCell.Utilities_3.6.R")
library(Seurat)
GT <- readRDS("~/GT.rds")
GT@misc <- NULL
GT <- UpdateSeuratObject(GT)
GT@assays$RNA@var.features <- gsub("_", "-", GT@assays$RNA@var.features)


ccg <- readLines("CellCycleGenes.txt")
ccg <- gsub("-", "_", ccg)
g1s <- list(ccg[1:86])
s <- ccg[87:172]
g2m <- ccg[173:252]
m <- list(ccg[253:336])
mg1 <- list(ccg[337:381])
GT <- CellCycleScoring(GT, s.features = s, g2m.features = g2m, 
                       set.ident = T)
pdf("GT_PhaseScored.pdf")
TSNEPlot(GT, cols = colors.use)
dev.off()

GT <- ScaleData(GT, vars.to.regress = c("nUMI", "S.Score", "G2M.Score"),
                features = GT@assays$RNA@var.features, verbose = T)
GT.pca <- TestPCA(GT)
GT <- RunPCA(GT, npcs = 9, features = GT@assays$RNA@var.features)
GT <- RunTSNE(GT, dims = 1:9)
pdf("GT_tSNE_Phase-regressed.pdf")
TSNEPlot(GT, cols = colors.use)
dev.off()

Idents(GT) <- GT[["ID"]]
pdf("GT_tSNE_Phase-regressed_Nodes.pdf")
TSNEPlot(GT, cols = colors.use)
dev.off()

genes <- c("Mki67", "Pcna", "Ccnd1", "Ccnd2", "Gli1", "Atoh1", "Barhl1", "Cntn2", "Rbfox3", "Meg3")
p <- list()
for(i in 1:10){
  message(genes[i])
  p[[i]] <- MultiFeaturePlot(GT, genes[i], colors = colors.use[i], 
                             pt.size = 1, scale.color = T)
}
pdf("GT_tSNE_Phase-regressed_Markers.pdf", width = 20, height = 11.25)
CombinePlots(plots = p, ncol = 4)
dev.off()
x11()
```

#SCRATCH
```{r}

source("~/SingleCell.Utilities.R")
Veh <- readRDS("~/Veh.rds")
GT <- readRDS("~/GT.rds")
WT <- readRDS("WT.rds")
GT@data <- GT@misc
WT@data <- WT@misc
Veh <- SubsetData(GT, subset.name = "Treatment", accept.value = "Vehicle")
Vis <- SubsetData(GT, subset.name = "Treatment", accept.value = "Vismodegib")
saveRDS(GT@dr$tsne@cell.embeddings, "GT_xy.rds")
saveRDS(WT@dr$tsne@cell.embeddings, "WT_xy.rds")
saveRDS(WhichCells(Veh), "Veh_Cells.rds")
saveRDS(WhichCells(Vis), "Vis_Cells.rds")

genes <- c('Amt', "Gcsh", "Gldc")

grep('Mat', rownames(GT@misc), value = T)
grep("Cd276", rownames(WT@data), value = T)
for(gene in genes){
  pdf(paste0('GT_', gene, '.pdf'))
  print(MultiFeaturePlot(GT, gene))
  dev.off()
  pdf(paste0('WT_', gene, '.pdf'))
  print(MultiFeaturePlot(WT, gene))
  dev.off()
  pdf(paste0('Veh_', gene, '.pdf'))
  print(MultiFeaturePlot(Veh, gene))
  dev.off()
  pdf(paste0('Vis_', gene, '.pdf'))
  print(MultiFeaturePlot(Vis, gene))
  dev.off()
}


```
